Rotations and Insecticide Resistance the story

### 2018-02-07 inst/documents/rotations_notes.Rmd
to pass check plus doc and add warning to shiny

*26/1/2018*

what to call new UI resistrot consistent with resistmixseq

@@

Explore idea from Rowland (1981) that resistance declines faster when it is mostly held by the RR (i.e. at higher allele frequencies)

>>>>

*26/1/2018*
new UI resistrot, similar name to resistmixseq

*1/2/2018*

I want to create a figure that shows effect of untreated area, refugia
Can I do this in ggplot2, or do it in powerpoint ?
see : resistance-dispersal-dilution-figure.pptx

How to create a greater effect of dispersal, reduce the coverage.

run_rot(n_insecticides = 1)
Error in RAF1gen[, , "intervention"] : incorrect number of dimensions
Called from: rot_migrate(RAF[, , , gen], migration = migration, coverage = coverage)

but this is OK
run_rot(n_insecticides = 1, coverage=1)

I suspect problem is with dropping dimensions in rot_migrate when there's just one insecticide
For now just force n_insecticides > 1 from the UI

@@

~ can we do cross resistance within the rotations model ? i.e. that resistance to one insecticide also provides some protection against another ?

~ something not right, when run with coverage=0 still get increase in resistance in treated areas, even though technically there is no treated area, maybe I just need to force coverage to be > 0 :
run_rot( n_insecticides = 3 , max_gen = 150 , start_freqs = 0.01 , rot_interval = 0 , eff = 0.8 , dom_sel = 0.5 , dom_cos = 0.5 , rr = 0.5 , expo_hi = 0.5 , coverage = 0 , migration = 0.01 , cost = 0.01 , logy = TRUE no_r_below_start = TRUE min_rwr_interval = 5 )

~ add error-check to run_rot if n.insecticides=1 & migration > 0

Maybe explore idea from Rowland (1981) that resistance declines faster when it is mostly held by the RR (i.e. at higher allele frequencies)

### 2018-02-07 inst/documents/rotations_story.Rmd
to pass check plus doc and add warning to shiny

library(knitr)
#https://stackoverflow.com/a/36234023/1718356 for fig.pos = 'h'
opts_chunk$set(fig.height=3, fig.width=7, fig.pos = 'h', echo=FALSE, warning=FALSE, message=FALSE)
# opts_chunk$set(dev="tiff",
#                dev.args=list(compression="lzw"),
#                dpi=300,
#                cache=FALSE,
#                fig.path='pap2figs/')
```

@@

```{r, eval=TRUE, fig.height=2.5, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A sequence with 1 percent dispersal between treated and untreated areas of equal size (no resistance costs)."}

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0, coverage=0.5, migration = 0.01)

@@

```{r, eval=TRUE, fig.height=2.5, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A 1 year rotation with 1 percent dispersal between treated and untreated areas of equal size (no resistance costs)."}

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0, coverage=0.5, migration = 0.01)

@@

```{r, eval=TRUE, fig.height=2.5, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A sequence with dispersal between treated and untreated areas and resistance cost of 0.005."}

#upped max_gen because migration and cost decrease rise in resistance
dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0.005, coverage=0.5, migration = 0.01)

@@

```{r, eval=TRUE, fig.height=2.5, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A 1 year rotation with with dispersal between treated and untreated areas and resistance cost of 0.005."}

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0.005, coverage=0.5, migration = 0.01)

@@

>>>>

library(knitr)
#https://stackoverflow.com/a/36234023/1718356 for fig.pos = 'h'

opts_chunk$set(fig.height=3, fig.width=7, fig.pos = 'h', echo=FALSE, warning=FALSE, message=FALSE)

# #these options make the pdf fail but do create the tiffs
opts_chunk$set(fig.height=3, fig.width=7, fig.pos = 'h', echo=FALSE, warning=FALSE, message=FALSE,
               dev="tiff",
               dev.args=list(compression="lzw"),
               dpi=300,
               cache=FALSE,
               fig.path='figs/')
```

@@

```{r, eval=TRUE, fig.height=2.5, fig.width=5, fig.show='hold', fig.align='left', fig.cap="A sequence with 2 percent dispersal between treated and untreated areas of equal size (no resistance costs)."}

dfr <- run_rot(n_insecticides=2, max_gen = 130, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0, coverage=0.5, migration = 0.02)

@@

```{r, eval=TRUE, fig.height=2.5, fig.width=5, fig.show='hold', fig.align='left', fig.cap="A 1 year rotation with 2 percent dispersal between treated and untreated areas of equal size (no resistance costs)."}

dfr <- run_rot(n_insecticides=2, max_gen = 130, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0, coverage=0.5, migration = 0.02)

\newpage
### more insecticides

```{r, eval=TRUE, fig.height=5, fig.width=5, fig.show='hold', fig.align='left', fig.cap="A sequence with 10 percent coverage and 5 perecnt dispersal."}

dfr <- run_rot(n_insecticides=4, max_gen = 130, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0, coverage=0.1, migration = 0.05)

```{r, eval=TRUE, fig.height=5, fig.width=5, fig.show='hold', fig.align='left', fig.cap="A 1 year rotation with 1 percent dispersal between treated and untreated areas of equal size (no resistance costs)."}

dfr <- run_rot(n_insecticides=4, max_gen = 130, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0, coverage=0.1, migration = 0.05)

@@

```{r, eval=TRUE, fig.height=2.5, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A sequence with dispersal between treated and untreated areas and resistance cost of 0.05."}

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=0, expo_hi=0.5, eff=0.8, cost=0.05, coverage=0.5, migration = 0.01)

@@

```{r, eval=TRUE, fig.height=2.5, fig.width=7, fig.show='hold', fig.align='left', fig.cap="A 1 year rotation with with dispersal between treated and untreated areas and resistance cost of 0.05."}

dfr <- run_rot(n_insecticides=2, max_gen = 200, rot_interval=10, expo_hi=0.5, eff=0.8, cost=0.05, coverage=0.5, migration = 0.01)

@@

knitr::knit_exit() 
### plots after this don't show much interesting
